### 2022-04-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@934aa5f485bf2bc6afb6fe14cb605aefcb6df284 🚀

In order to turn the hypotheses based on the Geographic Mosaic Theory of
Coevolution into a measure of risk, we overlapped three components:
viral sharing, i.e.~the chance that two bats will share viruses overall;
Local Contribution to Beta Diversity, i.e.~the fact that a bat community
is compositionally unique compared to the average compositional
similarity across the entire system; finally, the phylogenetic
diversity, i.e.~how dispersed the bats in a location are within the tree
of life. These results are presented using an additive color mapping in
Figure xx, and lead to the definition of broad biogeographic regions of
risk, where the same color represents the same type of risk. Pairwise
maps of the three components are present in supplementary materials.

@@

@@

>>>>

In order to turn the hypotheses based on the Geographic Mosaic Theory of
Coevolution into a measure of risk, we overlapped three components of
spillover risk: viral sharing, \emph{i.e.} the chance that two bats will
share viruses overall; Local Contribution to Beta Diversity, \emph{i.e.}
the fact that a bat community is compositionally unique compared to the
average compositional similarity across the entire system; finally, the
phylogenetic diversity, \emph{i.e.} how dispersed the bats in a location
are within the tree of life. These results are presented using an
additive color mapping in Figure xx, and lead to the definition of broad
biogeographic regions of risk, where the same color represents the same
type of risk. Pairwise maps of the three components are present in
supplementary materials.

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:trivariate}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:risk}{%
\centering
\includegraphics{figures/risk_map.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:risk}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:compound}{%
\centering
\includegraphics{figures/risk_compounded.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:compound}
}
\end{figure}
